Wireless Automobile Detection, License Plate Processing, and Data Availability Network

### 2014-05-01 paper/paper.tex
Added image processing future work

\subsection{Real-world Deployment}
Due to the fact that this project was time-constrained, we were unable to test our system in a real-world environment. We had initially planned to deploy a working version of our system on two parking lots on the CSM campus. Even though we never deployed our system, we were able to get everything connected together as described in section 2, so that data collected by the sensors flowed all the way up through the system and was displayed in the web application. Our plans for a future deployment are as follows: ACMx and members from our group plan to deploy a version of our system at the CTLM Upper and Lower parking lots at CSM. These lots were chosen because of their accessible location, unobstructed visibility from a campus structure, and frequent use. Both parking lots have one entryway, each of which will be equipped with an automobile detection subsystem. The junction between the two lots is also of interest, because we want to know when a car moves from the upper lot to the lower lot, and vice versa. The locations of the entrances and junction are shown in Figure \ref{fig:deployment}. The locations for the three sensor nodes benefit from having a clear view of the sky for increased photovoltaic efficiency.
\begin{figure}
\begin{center}
\includegraphics[width=5in]{deployment}
\end{center}
\caption{Deployment Location}
\label{fig:deployment}
\end{figure}

@@

@@

Kevin Emery worked with the image processing on the image acquisition Raspberry Pis. He wrote Python scripts that make use of the OpenCV library to process images, which mainly includes cropping and compressing to sizes that are reasonable for transmission over the XBee radio. He explored contour mapping as one possibility for reducing image size while still maintaining a readable license plate, but found the current OpenCV implementation to be ineffective given the provided images.

>>>>

\subsection{Real-world Deployment}
Due to time-constraints, we were unable to test our system in a real-world environment. We had initially planned to deploy a working version of our system on two parking lots on the CSM campus. Even though we never deployed our system, we were able to get everything connected together as described in section 2, so that data collected by the sensors flowed all the way up through the system and was displayed in the web application. Our plans for a future deployment are as follows: ACMx and members from our group plan to deploy a version of our system at the CTLM Upper and Lower parking lots at CSM. These lots were chosen because of their accessible location, unobstructed visibility from a campus structure, and frequent use. Both parking lots have one entryway, each of which will be equipped with an automobile detection subsystem. The junction between the two lots is also of interest, because we want to know when a car moves from the upper lot to the lower lot, and vice versa. The locations of the entrances and junction are shown in Figure \ref{fig:deployment}. The locations for the three sensor nodes benefit from having a clear view of the sky for increased photovoltaic efficiency.
\begin{figure}
\begin{center}
\includegraphics[width=5in]{deployment}
\end{center}
\caption{Deployment Location}
\label{fig:deployment}
\end{figure}

@@

\subsection{Image Acquisition and Processing}
The current solution for imaging is solely based on the limited set of test images we were able to acquire, and is likely not robust enough for a full deployment. Once a successful deployment has been achieved, the image acquisition time needs to be fine-tuned so the license plate is always captured in the image. If the greedy cropping strategy for image processing is maintained, then it can be expanded upon to eliminate pieces on the left and right of the car in order to further reduce file size.

While contour mapping proved to be unsuccessful when processing the full images, further work should be done, once image acquisition has been fine-tuned, to crop the image and then apply contour mapping to the cropped image. The method failed originally because the license plate was not featured prominently in the image, and cropping the image more effectively could greatly help the contours of the license plate better stand out.

@@

Kevin Emery worked with the image processing on the image acquisition Raspberry Pis. He wrote Python scripts that make use of the OpenCV library to process images, which mainly includes cropping and compressing to sizes that are reasonable for transmission over the XBee radio. He explored contour mapping as one possibility for reducing image size while still maintaining a readable license plate, but found the current OpenCV implementation to be ineffective given the provided images. His work is detailed in sections 3.2 and 4.1
